---
title: "homework_5"
author: "Isabella Muratore"
date: "November 12, 2017"
output: html_document
---
# homework #5

## Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your ββ coeffiecients (slope and intercept). 
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)

m <- lm(data = d, log(HomeRange_km2) ~ log(Body_mass_female_mean))

summary(m)
```
### β0 = -9.44123
### β1 = 1.03643



## Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each ββ coefficient.

```{r}
#from R in action
bs <- function(formula, data, indices) {
  d <- data[indices,]
  fit <- lm(formula, data=d)
  return(coef(fit))
}


library(boot)
set.seed(1234)
results <- boot(data=d, statistic=bs, R=1000, formula= log(HomeRange_km2) ~ log(Body_mass_female_mean))

print(results)


```
## Estimate the standard error for each of your ββ coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your ββ coefficients based on the appropriate quantiles from your sampling distribution.

```{r}

boot.ci(results, type="bca", index=1)

boot.ci(results, type="bca", index=2)

```

## How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

```{r}

m <- lm(data=d, log(HomeRange_km2) ~ log(Body_mass_female_mean))

summary(m)

```

## How does the latter compare to the 95% CI estimated from your entire dataset?

```{r}

confint(m)

```

## EXTRA CREDIT: + 2

##Write a FUNCTION that takes as its arguments a dataframe, “d”, a linear model, “m” (as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level, “conf.level” (with default = 0.95), and a number of bootstrap replicates, “n” (with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.

```{r}
fun <- function(d, m, conf.level=0.95, n=1000){
  library(broom)
  category <- c("1name_B0", "2name_B1", "3B0", "4B1", "5B0_sample_SE", "6B1_sample_SE", "7B0_sample_lower_CI", "8B0_sample_upper_CI", "9B1_sample_lower_CI", "10B1_sample_upper_CI", "11B0_u", "12B1_u", "13B0_boot_SE", "14B1_boot_SE", "15B0_boot_lower_CI", "16B0_boot_upper_CI", "17B1_boot_lower_CI", "18BI_boot_upper_CI")
  bs <- function(formula, data, indices) {
    d <- data[indices,]
    fit <- lm(formula, data=d)
    return(coef(fit))
  }
  value <- c("intercept")
  name <- gsub("^.*\\~","", m)
  value <- c(value, name)
  
  library(boot)
  mod <- lm(data=d, m)
  modd <- summary(mod)
  moddd <- tidy(modd)
  #B0 sample
  value <- c(value, moddd[1,2])
  #B1 sample
  value <- c(value, moddd[2,2])
  #B0 sample se
  value <- c(value, moddd[1,3])
  #B1 sample se
  value <- c(value, moddd[2,3])
  
  #FIXXX
  co <- lm(data=d, m)
  con <- confint(co)
  conn <- tidy(con)
  #B0 sample lower
  value <- c(value, conn[1,2])
  #B0 sample upper
  value <- c(value, conn[1,3])
  #B1 sample lower
  value <- c(value, conn[2,2])
  #B1 sample upper
  value <- c(value, conn[2,3])
  
  set.seed(1234)
  results <- boot(data=d, statistic=bs, R=n, formula=m)
  t <- tidy(results)
  #B0 u
  value <- c(value, t[1,2])
  #B1 u
  value <- c(value, t[2,2])
  #B0 boot se
  value <- c(value, t[1,4])
  #B1 boot se
  value <- c(value, t[2,4])
  
  #FIX
  b <- tidy(results, conf.int=TRUE, conf.level=0.95, conf.method = "bca")
  #B0 boot lower
  value <- c(value, b[1,5])
  #B0 boot upper
  value <- c(value, b[1,6])
  #B1 boot lower
  value <- c(value, b[2,5])
  #B1 boot upper
  value <- c(value, b[2,6])
  df <- rbind(category, value)
  dff <- data.frame(df)
  return(dff)
}

```

##EXTRA EXTRA CREDIT: + 1

##Graph each beta value from the linear model and its corresponding mean value, lower CI and upper CI from a bootstrap as a function of number of bootstraps from 10 to 200 by 10s. HINT: the beta value from the linear model will be the same for all bootstraps and the mean beta value may not differ that much!
